---
output: word_document
params:
  dir:
    value:x
  file:
    value: x
---

```{r setup, include=FALSE}
tryCatch({
  #Specify the output directory of the images
  knitr::opts_chunk$set(echo = TRUE,warning=FALSE,fig.path = paste0(params$dir,"/images/"))
  
  #Import libraries
  source(paste0(".","/functions/importLibrary.R"))
  
  #Remove the images folder which was generated before
  unlink(paste0(params$dir,"/images"), recursive = TRUE)
  unlink(paste0(params$dir,"/strategy-statistics.json"),recursive = TRUE)
  
  #Read price series from json file and make them ready to use
  source(paste0(".","/functions/getPriceSeries.R"))
  
  #Initialize intermediate file to keep the names of images
  imageNameMapping = data.frame(From = "", To = "")
},error = function(e){
  print("Setup Failed.")
})


```

<style>
  .col1 {
    columns: 1 1200;         /* number of columns and width in pixels*/
    -webkit-columns: 1 1200; /* chrome, safari */
    -moz-columns: 1 1200;    /* firefox */
  }
  .col1 table{
    width: 900px;
    font-size: 150%;
    font-family: "Open Sans Condensed";
  }
  .col3 {
    columns: 3 1200px;
    -webkit-columns: 3 1200px;
    -moz-columns: 3 1200px;
  }
  .col3 img{
    width: 300px;
    height: auto;
  }
  .col3 table{
    width: 900px;
    font-family: "Open Sans Condensed";
  }
  .col2 {
    columns: 3 1200px;
    -webkit-columns: 3 1200px;
    -moz-columns: 3 1200px;
    margin-left: 7%;
  }
  .col2 img{
    width: 400px;
    height: auto;
  }
  .col2 table{
    width: 900px;
  }
  	
  .dygraph-legend {
    background: transparent !important;
    left: 600px !important;
    top: 160px !important;
  }
  
  a:link {
     color:black;
  }
  
  sup {
     font-family: "Open Sans Condensed";
  }
  
<!--   table, th, td { -->
<!--     border: 1px solid black; -->
<!--     border-collapse: collapse; -->
<!-- } -->

</style>  

<div class="col1">
```{r one-column-1, results='asis', echo=FALSE, out.extra=''}
cat("<table class='container'>")
cat("<tr align='center'>")
cat("<th width='100%'>")
cat("Cumulative Returns")
cat("</th></tr>")
cat("</table>")
```
</div>

<div class="col1">
```{r CumulativeReturn, echo=FALSE,warning=FALSE,fig.width=11.5, fig.height=2.5,message=FALSE,results='asis', out.extra=''}
#Cumulative return chart
tryCatch({
  source(paste0(".","/functions/cumulativeReturn.R"))
  imageNameMapping = rbind(imageNameMapping,data.frame(From = "CumulativeReturn-1.png", 
                                                       To = "cumulative-return.png"))
},error = function(e){
  print("Cumulative Return Failed.")
})

```
</div>

<div class="col1">
```{r one-column-2, results='asis', echo=FALSE, out.extra=''}
cat("<table class='container'>")
cat("<tr align='center'>")
cat("<th width='100%'>")
cat("Daily Returns")
cat("</th></tr>")
cat("</table>")
```
</div>

<div class="col1">
```{r DailyReturns, echo=FALSE,warning=FALSE,fig.width=11.5, fig.height=2.5,message=FALSE,results='asis', out.extra=''}
#Daily return chart
tryCatch({
  source(paste0(".","/functions/dailyReturn.R"))
  imageNameMapping = rbind(imageNameMapping,data.frame(From = "DailyReturns-1.png", To = "daily-returns.png"))
},error = function(e){
  print("Daily Return Failed.")
})

```
</div>

<div class="col1">
```{r one-column-3, results='asis', echo=FALSE, out.extra=''}
cat("<table class='container'>")
cat("<tr align='center'>")
cat("<th width='100%'>")
cat("Top 5 Drawdown Period")
cat("</th></tr>")
cat("</table>")
```
</div>

<div class="col1">
```{r Drawdowns, echo=FALSE,warning=FALSE,fig.width=11.5, fig.height=2.5,message=FALSE,results='asis', out.extra=''}
#Drawdown chart
tryCatch({
  source(paste0(".","/functions/drawdown.R"))
  imageNameMapping = rbind(imageNameMapping,data.frame(From = "Drawdowns-1.png", To = "drawdowns.png"))
},error = function(e){
  print("Drawdowns Failed.")
})

```
</div>
<br></br>
<div class="col3">
```{r three-column-1, results='asis', echo=FALSE, out.extra=''}
cat("<table class='container'>")
cat("<tr align='center'>")
cat("<th width='35%'>")
cat("Monthly Returns(%)")
cat("</th><th width='30%'>")
cat("Annual Returns(%)")
cat("</th><th width='35%'>")
cat("Distribution of Monthly Returns")
cat("</th></tr>")
cat("</table>")
```
</div>

<div class="col3">
```{r Returns, echo=FALSE,warning=FALSE,message=FALSE}  
#Monthly return chart
tryCatch({
  source(paste0(".","/functions/monthlyReturn.R"))
  imageNameMapping = rbind(imageNameMapping,data.frame(From = "Returns-1.png", To = "monthly-returns.png"))
},error = function(e){
  print("Monthly Return Failed.")
})

#Yearly return chart
tryCatch({
  source(paste0(".","/functions/yearlyReturn.R"))
  imageNameMapping = rbind(imageNameMapping,data.frame(From = "Returns-2.png", To = "annual-returns.png"))
},error = function(e){
  print("Yearly Return Failed.")
})

#Monthly return distribution chart
tryCatch({
  source(paste0(".","/functions/monthlyReturnDistribution.R"))
  imageNameMapping = rbind(imageNameMapping,data.frame(From = "Returns-3.png", 
                                                       To = "distribution-of-monthly-returns.png"))
},error = function(e){
  print("Monthly Return Distribution Failed.")
})


```
</div>

<div class="col3">
```{r Event, echo=FALSE,warning=FALSE,message=FALSE,results='asis', out.extra=''}  
#Event Charts
tryCatch({
  source(paste0(".","/functions/event.R"))
},error = function(e){
  print("Event Charts Failed.")
})


```
</div>


<div class="col1">
```{r RollingPortfolioBetaToEquity, echo=FALSE,warning=FALSE,fig.width=11.5, fig.height=2.5,message=FALSE,results='asis', out.extra=''}
#Rolling Beta chart
tryCatch({
  source(paste0(".","/functions/rollingBeta.R"))
  
},error = function(e){
  print("RollingPortfolioBeta Failed.")
})


```
</div>


<div class="col1">
```{r RollingSharpeRatio(6-month), echo=FALSE,warning=FALSE,fig.width=11.5, fig.height=2.5,message=FALSE,results='asis', out.extra=''}
#Rolling Sharpe Ratio chart
tryCatch({
  source(paste0(".","/functions/rollingSP.R"))
  
},error = function(e){
  print("RollingSharpeRatio Failed.")
})


```
</div>


<div class="col1">
```{r NetHoldings, echo=FALSE,warning=FALSE,fig.width=11.5, fig.height=2.5,message=FALSE,results='asis', out.extra=''}
#Net Holdings chart
tryCatch({
  source(paste0(".","/functions/netHoldings.R"))
  imageNameMapping = rbind(imageNameMapping,data.frame(From = "NetHoldings-1.png", To = "net-holdings.png"))
},error = function(e){
  print("NetHoldings Failed.")
})


```
</div>


<div class="col1">
```{r Leverage, echo=FALSE,warning=FALSE,fig.width=11.5, fig.height=2.5,message=FALSE,results='asis', out.extra=''}
#Leverage chart
tryCatch({
  source(paste0(".","/functions/leverage.R"))
  imageNameMapping = rbind(imageNameMapping,data.frame(From = "Leverage-1.png", To = "leverage.png"))
},error = function(e){
  print("Leverage Failed.")
})


```
</div>

<div class="col3">
```{r AssetAllocation, echo=FALSE,warning=FALSE,message=FALSE,results='asis', out.extra=''} 
#Asset Allocation charts
tryCatch({
  source(paste0(".","/functions/assetAllocation.R"))
},error = function(e){
  print("AssetAllocation Failed.")
})


```
</div>


<div class="col1">
```{r one-column-4, results='asis', echo=FALSE, out.extra=''}
cat("<table class='container'>")
cat("<tr align='center'>")
cat("<th width='100%'>")
cat("Return Prediction")
cat("</th></tr>")
cat("</table>")
```
</div>

<div class="col1">
```{r ReturnPrediction, echo=FALSE,warning=FALSE,fig.width=11.5, fig.height=2.5,message=FALSE,results='asis', out.extra=''}
tryCatch({
  source(paste0(".","/functions/returnPrediction.R"))
  imageNameMapping = rbind(imageNameMapping,data.frame(From = "ReturnPrediction-1.png", 
                                                       To = "return-prediction.png"))
},error = function(e){
  print("ReturnPrediction Failed.")
})



```
</div>

```{r image_output, echo=FALSE,warning=FALSE,message=FALSE}
#Write the intermediate file
tryCatch({
  imageNameMapping = imageNameMapping[-1,]
  write.csv(imageNameMapping,paste0(params$dir,"/images/imageNameMapping.csv"))
},error = function(e){
  print("Image Output Failed.")
})


```

```{r json_table, echo=FALSE,warning=FALSE,message=FALSE}  
#Calculate strategy statistics and wirte json file
tryCatch({
  source(paste0(".","/functions/outputJson.R"))
}, error = function(e){
  print("Json Output Failed.")
}
)

```

<br></br>
<div class="col1">
```{r footnote, echo=FALSE,warning=FALSE,fig.width=11.5, fig.height=2.5,message=FALSE,results='asis', out.extra=''}
#Footnote in the html

cat("<hr></hr>")
index_array = index_array[! index_array %in% length(titles)]
for(i in 1:length(index_array))
{
  cat("<sup>")
  cat(i)
  cat(paste0(". [From ",startDate[index_array[i]]," To ",endDate[index_array[i]]
             ,"] ",footnotes[index_array[i]],"</sup><br>"))
}
```
</div>



